---
title: "Lab 6 - Finding Help"
author: "Your Group Members' Names"
date: "Due: October 8 by 5pm"
output: html_document
---

```{r}

```


Let's revisit the data from Lab 4 on the rate of deaths by age/gender 
(per 100,000 population) for people killed in crashes involving a driver 
with BAC =>0.08%, for years 2012 and 2014.  

# Difference in Means or the Mean of the Differences? 

In Lab 4 we considered the difference in fatality rate for every state in 2012 
verses 2014. To compare these rates, we used a difference in means. However, 
we could (should) have used the mean of the differences.   

__1. Why could we analyze these data as paired?__  


</br>
</br>

# Data Cleaning 

To analyze these data as paired, we need to carry out the following steps:  

* grab the columns we were interested in   
* create a new variable that is the difference between 2012 and 2014 fatality rates  
* filter out any missing values for these differences  

The code below attempts to carry out this procedure. 

```{r}

drunk_diff <- drunk %>% 
  filter(`All Ages, 2012`, `All Ages, 2014`, State) %>%  
  mutate_at(diff, `All Ages, 2012` - `All Ages, 2014`) %>% 
  filter(is.na(diff) == FALSE)
  
```  


__2. What error do you get when you run this code chunk? Why are you getting this error?__ 



</br> 

Add what you believe will fix this error to the `R` code chunk at the beginning 
(top) of the Markdown file.  

Run the line of code you added. Now re-run the code chunk above. 


__3. What error do you get now? Why are you getting this error?__ 


</br> 

Add what you believe will fix this error to the `R` code chunk at the beginning 
(top) of the Markdown file.  

Run the line of code you added. Now re-run the code chunk above. 

</br>

__Bonus:__ If I load my dataset into `R` using the "Import Dataset" button, what
will happen when I knit?


</br>

__4. What error do you get now? Why are you getting this error?__ 


</br> 

# Finding Help  

It seems that the code is using a function we have not explored before. It 
would be great if we could look up what this function is doing!  

One of the chief reasons for `R`'s religious following is its wonderful 
documentation. If you know a function does what you want (say find the 
variance),but are not quite sure how it's spelled, what arguments it takes, or 
what package it lives in, don't fret! The `?` and `help()` commands are very 
powerful. For functions, placing the `?` before the name, will tell `R` to 
search for that name in all of the functions, in all of the packages you have 
installed.  

* If it finds _one_ __identical match__, it will display the help file for that 
function in the Help tab in the bottom-right corner.  
* If it finds _more than one_ __identical match__, it will display the functions,
in their respective packages, that you have to choose from.  
* If it find _no_ __identical match__, it will tell you that "`No documentation 
for ____ in specified packages and libraries:,`" and suggests you use a `??` 
instead.  
    
    + A `??` in front of the function name will search __all of `R`__ for named 
    functions similar to what you typed.  
    + The output will tell you what package the function is in, as well as the 
    function's name (`package::function`).  


__5. Find the help file for the `mutate_at()` function.__ 
__What package is this function from? What function is it a variant of?__ 



</br> 


The help page for functions is broken down into sections:  

* Description: An extended description of what the function does.   
* Usage: The arguments of the function and their default values.     
* Arguments: An explanation of the object each argument is expecting.  
* Details: Any important details to be aware of.    
* Value: The object the function returns.      
* See Also: Any related functions that may be useful.    
* Examples: Some examples for how to use the function.

## Function Arguments  

Arguments describe the details of what a function is to do. Some functions take 
arguments that are specified by the user, or, if left undeclared, take on 
default values. Arguments are sometimes given names (as seen in the help
file), but the arguments are assumed to follow the order the function 
expects if they are not named (also stated in the help file). When naming an 
argument, the name of the argument is followed by an `=` sign and then the value
of the argument. Notice that here we are using the `=` to declare what value 
each argument is taking on, we **are not** creating a new variable with that 
value assigned to it.   


__6. What are the first three arguments to the `mutate_at()` function?__  
__Do these arguments have names?__  
__What data type does each of these arguments take?__ 



</br> 

It seems like this is not quite the function we are looking for. We wish to 
create a new variable named `diff` that contains the difference in fatality 
rates between 2014 and 2012.  


__7. What function do you think would best tackle this problem?__  
__Find that function's help page and list:__ 


* The function's arguments:   



* The output of the function (i.e. what type of object gets returned):  



</br>

# Put It All Together  

__8. Based on your explorations, modify the code above to create the `drunk_diff` dataset.__ 
<!-- Change the code in the earlier code chunk, DO NOT make a new code chunk!  -->



__9. Create a plot of the differences in fatality rates between 2012 and 2014.__ 
__Make sure you axis have nice labels!__  




__10. Interpret what you see in the plot of the differences in fatality rates.__ 
__Use no more than 3 sentences!__ 




__11. Make sure that your lab report knits! Use the spell check and knit again!__ 

